---
knit: "bookdown::render_book"
title: '`r source(here::here("_common.R")); paste(study_name, "Correlates Analyses Report")`'  
author: '`r paste(study_name, "Biostatistics Team")`'
date: "`r format(Sys.time(), '%B %d, %Y')`"
documentclass: book
site: bookdown::bookdown_site
bibliography: [book.bib, packages.bib]
biblio-style: apalike
suppress-bibliography: true
link-citations: yes
colorlinks: yes
graphics: yes
lot: yes
lof: yes
always_allow_html: yes
header-includes:
   - \usepackage{eso-pic,graphicx,transparent,caption,pdflscape,titling} # keep titling last!
   - \usepackage[margin=1in]{geometry}
   - \usepackage{float}
   - \usepackage{subfig}
   - \usepackage{chngpage}
---





\textbf{Reproducibility Notice}

This project integrates the virtual environments framework provided by [the
`renv` package](https://rstudio.github.io/renv/) for computational
reproducibility. By taking this approach, all results are generated using a
consistent versioning of both R and several R packages. This version of the
report was built with `r R.version.string`, [pandoc](https://pandoc.org/)
version `r rmarkdown::pandoc_version()`, and the following R packages:

```{r pkg-list, echo=FALSE, results="asis"}
# borrowed from https://github.com/tidymodels/TMwR/blob/master/index.Rmd
deps <- desc::desc_get_deps()
pkgs <- sort(deps$package[deps$type == "Imports"])
pkgs <- sessioninfo::package_info(pkgs, dependencies = FALSE)
df <- tibble::tibble(
  package = pkgs$package,
  version = pkgs$ondiskversion,
  source = gsub("@", "\\\\@", pkgs$source)
)
knitr::kable(df, format = "markdown")
```

To get started with using this project and its `renv` package library, we
first recommend briefly reviewing the [`renv` collaboration
guide](https://rstudio.github.io/renv/articles/collaborating.html).

<!--chapter:end:index_cor.Rmd-->

<!-- ```{r, echo=FALSE} -->
<!-- here::i_am("cor_coxph/report.Rmd") -->
<!-- ``` -->



```{r, echo=FALSE, message=FALSE}
message("~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ running cor_coxph report ~~~~~~~~~~~~~~~~~~~~~~~~~")
```






<!-- latex variables that may be used in report_sub -->
<!-- \newif\ifCOVE -->
<!-- \newif\ifENSEMBLE -->



```{r, echo=FALSE, results='asis'}

covariates_adjusted = config$covariates
covariates_adjusted = sub("\\~\\.\\+","",covariates_adjusted)
covariates_adjusted = sub("_","",covariates_adjusted)

res = knitr::knit_child(c(here::here('cor_coxph', paste0('report_', TRIAL, '.Rmd'))), quiet = TRUE)
cat(res, sep = '\n')

```

<!--chapter:end:cor_coxph/report.Rmd-->

```{r, echo=FALSE, message=FALSE}
message("~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ running references ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~")
```



`r if (knitr::is_html_output()) '
# References {-}
'`

<!--chapter:end:references.Rmd-->

# Appendix

```{r, echo = FALSE, message = FALSE, warning = FALSE}
quiet <- capture.output({
  renv::activate(project = here::here())
  #source(here::here("_common.R"))
})
library(here)
library(digest)

# hash algorithm picked based on https://csrc.nist.gov/projects/hash-functions
hash_algorithm <- "sha256"


# get hash of commit at HEAD
commit_hash <- system("git rev-parse HEAD", intern = TRUE)    
# get hash of input processed data file based on chosen hashing algorithm
processed_file_digest <- digest(file = config$data_cleaned, algo = hash_algorithm)
    


```

* This report was built from the
  [`CoVPN/correlates_reporting`](https://github.com/CoVPN/correlates_reporting)
  repository with commit hash  
  `r system("git rev-parse HEAD", intern = TRUE)`.  
  A diff of the changes introduced by that commit may be viewed at  
  https://github.com/CoVPN/correlates_reporting/commit/`r system("git rev-parse HEAD", intern = TRUE)`


* The `r hash_algorithm` hash sum of the processed file,  
`r paste0(config$data_cleaned)`:  
`r processed_file_digest`

<!--chapter:end:appendix.Rmd-->

